Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-10 analysis/paper/paper.Rmd
clean up wording about software used in discussion
remove an errant "*"

Much of the software used are Free Open Source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
However, the top three most widely used software packages were not FOSS, limiting the ability of the authors to share workflows with others.
MEGA was the most widely cited software in this evaluation reflecting the wide spread use of sequence analysis in the field of plant pathology.
The second, third and fourth, and eighth most frequently cited software packages were all statistical programs.
SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R, the most frequently occurring FOSS, is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
The remainder of the top ten software packages we found were related to sequence analysis, *i.e.*, BLAST, Clustal and BioEdit, phylogenetic analysis MrBayes or the general-purpose spreadsheet program Excel®.
It is interesting to note however, that even with the popularity of Python in scientific programming, it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.

@@

There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
The first level is including tables of raw data or code with the paper as a supplemental file.
This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra*\* with reproducible examples for readers to refer to.
This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.

>>>>

Much of the software used are Free Open Source Software (FOSS) packages, which means that the workflow can easily be recreated by anyone with the proper skills in using the software.
However, the top three most widely used software packages were not FOSS, limiting the ability of the authors to share workflows with others.
MEGA was the most widely cited software in this evaluation reflecting the wide spread use of sequence analysis in the field of plant pathology.
The second, third and fourth, and eighth most frequently cited software packages were all statistical programs.
SAS remains firmly entrenched in the discipline as the choice of software for statistical analysis followed by SPSS but R, the most frequently occurring FOSS, is not far removed from SPSS in fourth place with Statistica and Genstat tied for eighth.
It is interesting to note however, that even with the popularity of Python in scientific programming, it only appears in the survey twice in 2020 for both articles, not enough times to be in the top 10 most-cited.

@@

There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
The first level is including tables of raw data or code with the paper as a supplemental file.
This is suitable for studies that may have a small data set or simple analysis or for demonstrations purposes as @Madden2015 demonstrate in their discussion regarding the use of $P$ values in statistical analyses where they supply an *e-**X**tra* with reproducible examples for readers to refer to.
This allows the reader to quickly view the extra materials and a DOI is assigned as a part of the article itself.
